New Biomass Pools Workflow

### 2023-10-07 NewBiomassPoolsWorkflow.Rmd
got biopools integrated

```{r}
  # biomass at agecl at full resolution (all polygons and layers)
  #truebio_ss <- omlist$truth$biomass_ages[omlist$truth$biomass_ages$species %in% species_ss,]
```

@@

>>>>

@@

Decision: leave the `truebiopool_ss` object separate and process separately with a different survey config file and a separate call to `om_index`. Or just bind them together for biomass based surveys if it doesn't break anything.

Running `om_init` from the `mskeyrun` repo with my local NOBA atlantis outputs produced expected output:

> NOBAom <- om_init(here("data-raw/simulated-data/config/NOBA_sacc38Config.R"))
[1] "Read /Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38/nordic_runresults_01.nc successfully"
[1] "Read /Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38/nordic_runresults_01.nc successfully"
[1] "Read /Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38/nordic_runresults_01.nc successfully"
[1] "Read /Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38/nordic_runresults_01PROD.nc successfully"
[1] "Read /Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38/nordic_runresults_01PROD.nc successfully"
[1] "Read /Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38/nordic_runresults_01.nc successfully"
[1] "Read /Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38/nordic_runresults_01CATCH.nc successfully"
[1] "Read /Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38/nordic_runresults_01CATCH.nc successfully"
[1] "Read /Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38/nordic_runresults_01CATCH.nc successfully"
[1] "Read /Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38/nordic_runresults_01ANNAGEBIO.nc successfully"
[1] "Read /Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38/nordic_runresults_01ANNAGECATCH.nc successfully"
[1] "Read /Users/sarah.gaichas/Documents/0_Data/ms-keyrun/simulated-data/atlantisoutput/NOBA_sacc_38/nordic_runresults_01ANNAGECATCH.nc successfully"
> NOBAom$truth$biomass_pools
               species agecl time polygon     atoutput
1             Ben_bact     1    0       1 1.376317e+05
2        Detrivore_ben     1    0       1 1.088091e+05
3             Dinoflag     1    0       1 1.312067e+04
4      Gel_zooplankton     1    0       1 1.569070e+05
5              Lab_det     1    0       1 2.581300e+07
6         Large_phytop     1    0       1 3.268895e+05
7    Large_zooplankton     1    0       1 4.772586e+05
8   Medium_zooplankton     1    0       1 1.118751e+06
9             Pel_bact     1    0       1 3.268895e+04
10       Predatory_ben     1    0       1 1.088091e+05
11             Ref_det     1    0       1 8.904920e+06
12        Small_phytop     1    0       1 3.280167e+05
13   Small_zooplankton     1    0       1 9.152906e+05
14             Sponges     1    0       1 4.621541e+05
15            Ben_bact     1    1       1 8.875378e+05
16     Benthic_filterf     1    1       1 1.163897e-04
17             Carrion     1    1       1 1.700432e-10
18              Corals     1    1       1 1.148013e-04
19       Detrivore_ben     1    1       1 1.096034e+05
20            Dinoflag     1    1       1 4.509383e+01
21     Gel_zooplankton     1    1       1 1.563221e+05
22           King_crab     1    1       1 0.000000e+00
23             Lab_det     1    1       1 8.511963e+07
24        Large_phytop     1    1       1 8.999719e+03
25   Large_zooplankton     1    1       1 5.237310e+05
26  Medium_zooplankton     1    1       1 5.390765e+06
27            Pel_bact     1    1       1 1.230456e+06
28       Predatory_ben     1    1       1 1.089640e+05
29             Ref_det     1    1       1 8.142682e+06
30        Small_phytop     1    1       1 1.177500e+03
31   Small_zooplankton     1    1       1 7.373987e+07
32             Sponges     1    1       1 4.647222e+05
```

Added lines to `om_species` to include the truebiopool outputs:

```{r, code = readLines("https://raw.githubusercontent.com/r4atlantis/atlantisom/dev/R/om_species.R"), eval=F}

Now test modified `om_species` in `mskeyrun` repo:

```
> NOBAom_fw <- om_species(fwspp$Name, NOBAom, save = FALSE) #save by hand, don't overwrite 11 species omlist_ss
> NOBAom_fw$truebiopool_ss
               species agecl time polygon     atoutput
1             Ben_bact     1    0       1 1.376317e+05
2        Detrivore_ben     1    0       1 1.088091e+05
3             Dinoflag     1    0       1 1.312067e+04
4      Gel_zooplankton     1    0       1 1.569070e+05
5              Lab_det     1    0       1 2.581300e+07
6         Large_phytop     1    0       1 3.268895e+05
7    Large_zooplankton     1    0       1 4.772586e+05
8   Medium_zooplankton     1    0       1 1.118751e+06
9             Pel_bact     1    0       1 3.268895e+04
10       Predatory_ben     1    0       1 1.088091e+05
11             Ref_det     1    0       1 8.904920e+06
12        Small_phytop     1    0       1 3.280167e+05
13   Small_zooplankton     1    0       1 9.152906e+05
14             Sponges     1    0       1 4.621541e+05
15            Ben_bact     1    1       1 8.875378e+05
16     Benthic_filterf     1    1       1 1.163897e-04
17             Carrion     1    1       1 1.700432e-10
18              Corals     1    1       1 1.148013e-04
19       Detrivore_ben     1    1       1 1.096034e+05
20            Dinoflag     1    1       1 4.509383e+01
21     Gel_zooplankton     1    1       1 1.563221e+05
22           King_crab     1    1       1 0.000000e+00
23             Lab_det     1    1       1 8.511963e+07
24        Large_phytop     1    1       1 8.999719e+03
25   Large_zooplankton     1    1       1 5.237310e+05
26  Medium_zooplankton     1    1       1 5.390765e+06
27            Pel_bact     1    1       1 1.230456e+06
28       Predatory_ben     1    1       1 1.089640e+05
29             Ref_det     1    1       1 8.142682e+06
30        Small_phytop     1    1       1 1.177500e+03
31   Small_zooplankton     1    1       1 7.373987e+07
32             Sponges     1    1       1 4.647222e+05
33            Ben_bact     1    2       1 3.080604e+06
34     Benthic_filterf     1    2       1 1.199844e-04
35             Carrion     1    2       1 1.698761e-10
36              Corals     1    2       1 1.168009e-04
```

Now try a new `om_index` that rbinds the truebio and truebiopool objects together for a biomass based survey

```{r, code = readLines("https://raw.githubusercontent.com/r4atlantis/atlantisom/dev/R/om_index.R"), eval=F}

It works as tested from the `mskeyrun` SimData.Rmd (both age structured and biopool groups are in the output):

```
> NOBAom_fw_ind$survObsBiomB$BTS_fall_allbox_effic1_fw[[1]] |> dplyr::group_by(species) |> dplyr::summarise(survBtot = sum(atoutput))
# A tibble: 40 × 2
   species         survBtot
   <chr>              <dbl>
 1 Beard_seal      8.14e+ 4
 2 Ben_bact        9.36e+12
 3 Benthic_filterf 7.86e+10
 4 Carrion         7.46e- 7
 5 Corals          3.19e+11
 6 Demersal_large  6.47e+ 6
 7 Demersals_other 1.81e+ 8
 8 Detrivore_ben   2.59e+10
 9 Dinoflag        1.31e+ 6
10 Fin_whale       3.87e+ 7
# … with 30 more rows
# ℹ Use `print(n = ...)` to see more rows
```

Plots of the new `mskeyrun::simSurveyIndexFW` object are [here](https://noaa-edab.github.io/RpathSim/ParametersforRpath.html).
